Covariate analysis of MSSM reprocessed counts (with TMM normalisation)

### 2017-01-25 code/Rmd/MSSM_RNASeq_Reprocessed_TMM_SVA_BinnedCDR.Rmd
Added markdown to process reprocessed RNASeq of MSSM samples with binned CDR using TMM and SVA normalization

knit2synapse::knitToFolderEntity(file = "./MSSM_RNASeq_Reprocessed_TMM_BinnedCDR.Rmd",
                                 parentId = "syn5570248",
                                 entityName = 'MSBB Reprocessed RNASeq TMM Binned CDR')
```

@@

thisFileName <- 'MSSM_RNASeq_Reprocessed_TMM_BinnedCDR.Rmd'

@@

tmp <- paste('Using following covariates in the final model:', modelStr, 'and Donor_ID as random effects')
```
`r tmp`
### Sanity Check
Residualise significant covariates using a linear model and find correlation between PCA of residuals with covariates
```{r residualSigCovars.ALL, fig.width=25, fig.height=12}
residualSigCovars[["PC_res"]][[2]]$plotData
```
Adding "BrodmannArea.Dx" back to the residuals
```{r addVarsBack}
varsToAddBackIn <-  grep("BrodmannArea.Dx", colnames(FIT$coefficients), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  t(data.matrix(DM1$design[,varsToAddBackIn]) %*% t(FIT$coefficients[,varsToAddBackIn]))
```

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'MSBB Reprocessed RNASeq TMM Binned CDR', parentId = parentId)
annotations(CODE) = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'Reprocessed RNAseq',

@@

  normalizationType	= 'TMM'
)
CODE <- synStore(CODE)

>>>>

knit2synapse::knitToFolderEntity(file = "./MSSM_RNASeq_Reprocessed_TMM_SVA_BinnedCDR.Rmd",
                                 parentId = "syn5570248",
                                 entityName = 'MSBB Reprocessed RNASeq TMM SVA Binned CDR')
```

@@

thisFileName <- 'MSSM_RNASeq_Reprocessed_TMM_SVA_BinnedCDR.Rmd'

@@

tmp <- paste('Using following covariates in the final model:', modelStr, 'and Donor_ID as random effects')
```
### SVA 
Estimate surrogate variables using SVA package
```{r sva}
MODEL0 = DM1$design[,-grep('BrodmannArea.Dx',colnames(DM1$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DM1$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]

## Calculate the number of surrogate variables
NUM.SV = sva::num.sv(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1,
                     method = 'be', seed = 123456, B = 30)

SURR.VAR = sva::sva(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, MODEL0,
                    n.sv = NUM.SV, B = 30)$sv

colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])
rownames(SURR.VAR) = rownames(DM1$design)

DM1$design = cbind(MODEL1, SURR.VAR)

# Re-estimate voom weights
VOOM.ADJUSTED.GENE_EXPRESSION = voom(TMM.GENE_EXPRESSION, design=DM1$design, plot=F, 
                                     block = COVARIATES$Donor_ID, correlation = correlation$cor)

# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION, 
                                              COVARIATES,
                                              'all adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
```

### Sanity Check
Residualise significant covariates using a linear model and find correlation between PCA of residuals with covariates
```{r residualSigCovars.ALL, fig.width=25, fig.height=12}
residualSigCovars[["PC_res"]][[2]]$plotData
```
Adding "BrodmannArea.Dx" back to the residuals
```{r addVarsBack}
varsToAddBackIn <-  grep("BrodmannArea.Dx", colnames(FIT$coefficients), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  t(data.matrix(DM1$design[,varsToAddBackIn]) %*% t(FIT$coefficients[,varsToAddBackIn]))
```

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'MSBB Reprocessed RNASeq TMM SVA Binned CDR', parentId = parentId)
annotations(CODE) = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'Reprocessed RNAseq',

@@

  normalizationType	= 'TMM and SVA'
)
CODE <- synStore(CODE)
